---
title: "ggplot1"
output: github_document
---
```{r}
library(tidyverse)
library(ggridges)
```

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

## Scatterplot

tmax vs. tmin

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + geom_point()
```

GGplot: give me a dataset, tell me what variables map to where then start stacking up geometries

Can save ggplots
```{r}
ggp_tmax_tmin =
  weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
```

## Let's fancy it up

Add...color? lines? other stuff?

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .3) + 
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```

geom_smooth: adds lines - drawing a line through the middle of the datapoints for each dataset
alpha blending: what degree of transparency do you want to have of the points
  alpha = .3 --> worked for points generated by this geometry (didn't impact the lines)
